Illusion Game Validation (Study 1)

### 2022-08-05 study1.Rmd
update RodFrame stim

@@

```{r message=FALSE, warning=FALSE}
# plot(estimate_density(dfraw[dfraw$Participant == "60684f29dbfe1bb2059e5e27_rkqoy", "RT"]))

# Dear participant, thank you for participating in our study. Unfortunately, our system detected multiple issues in your data (such as implausibly short responses, and random-like pattern of answers), which makes your data unusable. We understand that you might have been in a hurry or had some other issues, and kindly ask you to return your participation. We hope to open-up more slots in the future would you be interested to participate again.

# Dear participant, thank you for participating in our study. Unfortunately, our system detected multiple issues in your data (such as implausibly short responses, and random-like pattern of answers), which makes it unusable. We understand that you might have been in a hurry or had some other issues; we hope to open-up more slots in the future would you be interested to participate again.

outliers <- c(
  # Half of the trials have very short RT
  # Prolific Status: REJECTED
  "60684f29dbfe1bb2059e5e27_rkqoy",
  # Block n2 with very short RTs
  # Prolific Status: RETURNED
  "5e860198a846e30497df5189_6e43s",
  # Error rate of 46.2% and short RTs
  # Prolific Status: RETURNED
  "615f319bb341cf2f306d858d_qsaq5",
  # Error rate of 46.2%
  # Prolific Status: RETURNED
  "614f36fd81c78b7a125c4262_6ax4g",
  # Error rate of 47.9%
  # Prolific Status: REJECTED
  "61280140171ec546e87ed8cb_qdlgy",
  # Error rate of 42.1% and very large RT SD
  # Prolific Status: REJECTED
  "5d398380b37ab1000111fac3_2nxxh"
)
```

>>>>

# Transformation
df$Illusion_Difference_log <- log(1 + df$Illusion_Difference)
df$Illusion_Difference_sqrt <- sqrt(df$Illusion_Difference)
df$Illusion_Difference_cbrt <- round(df$Illusion_Difference**(1/3), 4)
df$Illusion_Strength_log <- sign(df$Illusion_Strength) * log(1 + abs(df$Illusion_Strength))
df$Illusion_Strength_sqrt <- sign(df$Illusion_Strength) * sqrt(abs(df$Illusion_Strength))
df$Illusion_Strength_cbrt <- sign(df$Illusion_Strength) * (abs(df$Illusion_Strength)**(1/3))

@@

```{r message=FALSE, warning=FALSE}
outliers <- c(
  # Half of the trials have very short RT
  # Prolific Status: REJECTED
  "60684f29dbfe1bb2059e5e27_rkqoy",
  # Block n2 with very short RTs
  # Prolific Status: RETURNED
  "5e860198a846e30497df5189_6e43s",
  # Error rate of 46.2% and short RTs
  # Prolific Status: RETURNED
  "615f319bb341cf2f306d858d_qsaq5",
  # Error rate of 46.2%
  # Prolific Status: RETURNED
  "614f36fd81c78b7a125c4262_6ax4g",
  # Error rate of 47.9%
  # Prolific Status: REJECTED
  "61280140171ec546e87ed8cb_qdlgy",
  # Error rate of 42.1% and very large RT SD
  # Prolific Status: REJECTED
  "5d398380b37ab1000111fac3_2nxxh"
)
```
